Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2023-05-09 write-up/fda-recurrent.tex
updated

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is point estimate for the complete-case analysis, while highlighted region are the model-based pointwise 95\% confidence intervals.}
\label{fig:edacc_estimate}
\end{figure}

\subsection{Accounting for missing data}
\label{sec:missingdata_heterogeneity}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint_bootstrap.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate_bs}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint_bootstrap.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate_bs}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is point estimate for the missing data analysis, while highlighted region are the boostrap and MI based pointwise 95\% confidence intervals.}
\label{fig:edacc_estimate_bs}
\end{figure}

>>>>

\begin{table}
\begin{tabular}{c c c c}
Delta & 5 & 15 & 30 \\ \hline
AIC & - & - & - \\
BIC & - & - & - \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/eda_coef_joint_bootstrap_Delta_15.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:eda_estimate}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint_bootstrap_Delta_15.png}
  \caption{Activity Index (AI)
}  \label{fig:acc_estimate}
\end{subfigure}
\caption{$\beta (t)$ for AI and EDA with 95\% CI; solid line is point estimate for the complete-case analysis, while highlighted region are the model-based pointwise 95\% confidence intervals.}
\label{fig:edacc_estimate}
\end{figure}

\subsection{Sensitivity analysis for window length}
\label{sec:missingdata_heterogeneity}

@@

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint_bootstrap_Delta_5.png}
  \caption{$\Delta = 5$ minutes}
  \label{fig:acc_estimate_bs_delta5}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/acc_coef_joint_bootstrap_Delta_30.png}
  \caption{$\Delta = 30$ minutes}
  \label{fig:acc_estimate_bs_delta30}
\end{subfigure}
\caption{$\beta (t)$ for ACC and EDA with 95\% CI; solid line is point estimate for the missing data analysis, while highlighted region are the boostrap and MI based pointwise 95\% confidence intervals.}
\label{fig:edacc_estimate_bs}
\end{figure}
